From Active Hostilities to Frozen Stalemates: Assessing the Role of External Support in Civil Conflict Dynamics

### 2023-11-30 paper.qmd
Manuscript notes

@@

@@

>>>>

- Frozen conflicts as a suboptimal solution to the contest between an incumbent and challenger.

@@

I model the onset of a frozen civil conflict using a bayesian probit regression where the unit analysis is civil conflict episodes, *i.e.*, contiguous years of active fighting within a conflict. The outcome variable, $y \in \{ 1, 2 \}$, is a binary indicator denoting the

@@

## List of Frozen Conflicts

## Simulation Based Calibration
